---
title: "MATH4753F25marissak"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MATH4753F25marissak}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753F25marissak)
```

# Introduction
The `MATH4753F25marissak` package provides tools for statistical analysis, bootstrapping, and visualization. It includes multiple functions and datasets designed to support coursework in MATH 4753.

# Datasets
This package includes two datasets:

- `fire`: [A dataset containing fire-related data, 15 rows and 2 variables]

- `ddt`: [A dataset containing measurements of DDT concentrations in the Tennessee River Valley, 144 rows and 6 columns]

```{r}
head(fire)
summary(fire)
```
```{r}
head(ddt)
summary(ddt)
```

# Functions 
This package includes 11 functions - four are described below:

- `mycurve`: [Function plots a normal distribution and shades the area up to a given value `a`]

- `Birthday`: [Function calculates the probability that at least two people in a group share a birthday]

- `mycltu`: [Function simulates the Central Limit Theorem using samples from a uniform distribution]

- `ntickets`: [Function calculates the maximum number of tickets to sell given seat capacity, show‑up probability, and acceptable overbooking risk]

```{r}
myncurve(mu = 100, sigma = 15, a = 120)
```
```{r}
Birthday(20:24)
```
```{r}
mycltu(n = 20, iter = 10000)
```
```{r, fig.width=7, fig.height=6}
ntickets(N = 400, gamma = 0.02, p = 0.95)
```

# Conclusion
This vignette demonstrates how the `MATH4753F25marissak` package can be used for probability visualization, simulation, and applied decision‑making. For more details, see the GitHub repository: https://github.com/yourusername/MATH4753F25marissak






